%\title{cover letter}
%
% See http://texblog.org/2013/11/11/latexs-alternative-letter-class-newlfm/
% and http://www.ctan.org/tex-archive/macros/latex/contrib/newlfm
% for more information.
%
\documentclass[12pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac}
 
\newlfmP{dateskipbefore=10pt}
\newlfmP{sigsize=40pt}
\newlfmP{sigskipbefore=0pt}
 
\newlfmP{Headlinewd=0pt,Footlinewd=0pt}
 
\namefrom{Braden Beck}
 
\addrto{%
Amazon San Luis Obispo
}
 
\dateset{Feb 1, 2021}
 
\greetto{I hereby tender my resignation,}
 
\closeline{Thanks for everything,}
 
\begin{document}
\begin{newlfm}
It is with a heavy heart and no small amount of remorse that I elect to inform you that I will be leaving my position at the company effective 2021-02-16T00:00:00Z. I have genuinely enjoyed my time spent working for Amazon's loyal customers, it's tenacious stakeholders, and it's excellent employees. Today I find myself working for the security team at Amazon Web Services, but I am forced to reconcile with the fact that this portion of the company is still part of the Amazon cooperation. While I can forgive most things, I never hold grudges, and I recognize that evil is in the action and not the actor, there is still a limit to my forgiveness. Sadly that limit has been reached. While 2020 brought about many changes, uncertainty, loss, hardship, it also brought with it opportunity. Amazon chose to use this opportunity to spend a record amount of capital on influencing US lawmakers and regulators. A company that already has millions of loyal customers across the world, whose CEO owns a international media cooperation on the side, spending this kind of capital on gaining political influence is deeply saddening to me. I cannot in good conscious continue to provide value to a company that chooses to exercise it's influence on my life even if I choose not to be a customer. Amazons customers choose to use Amazon because of the promises it keeps and the value it provides, but no one is required to use Amazon's services. Everyone who lives in the US is subject to it's laws whether or not they agree to them. The fact that a single cooperation has more control over those laws than the people it governs is the opposite of democracy, freedom, and the rule of law. No matter how benevolent it's intentions Amazon exercising it's power in the form of capital to influence the laws that not only govern it, but also people who may have never even heard of the company deprives the millions of citizens who don't use Amazon of their rights and freedoms and is fundamentally antithetical to Amazons own leadership principles. Paying to change the laws that it's own customers may have voted for is not customer obsession, it's not ownership, it's not thinking big or even delivering results, it's subverting the democratic process and suppressing and alienating people who are potential Amazon customers. It pains me to see the actions taken by the company become so antithetical to the principles it has taught me to value.
\end{newlfm}
\end{document}
